The ChEMBL database as Linked Open Data

### 2012-08-14 article.tex
Added some text on where the Details button points to

\begin{figure*}[!ht]
		\begin{center}
		\includegraphics[width=15cm]{citedin.png}
		\newline
		\caption[wee]{Screenshot of the CitedIn web service showing a paper cited 94671 times in the ChEMBL database.}
	\label{fig:citedin}
		\end{center}
\end{figure*}

@@

>>>>

\begin{figure*}[!ht]
		\begin{center}
		\includegraphics[width=15cm]{citedin.png}
		\newline
		\caption[wee]{Screenshot of the CitedIn web service showing a paper cited 94671 times in the ChEMBL database.
		   The \textit{Details} button on the webpage links to a ChEMBL webpage with detail on what parts of the database are
		   linked to that paper.}
	\label{fig:citedin}
		\end{center}
\end{figure*}

@@

The CitedIn summary for ChEMBL also provides a \textit{Details} button that links back to a ChEMBL webpage providing
a \textit{Document Report Card} showing in more detail what targets, assays, compounds, and activities in the database
are linked to that paper.
